Topology and experimental distinguishability

### 2017-11-25 Articles/TopologyAndExperimentalDistinguishability/article.tex
Adding two remarks

@@

>>>>

\begin{rem}
	Any scientific measurement can be formulated as an observation in the form above. For example, \emph{``the mass of the electron is 510,999 $\pm$ 0.5 eV"} places the value within the open set $U=(510,998.5 , 510,999.5)$.
\end{rem}

@@

\begin{rem}
	Any scientific law can be seen as the relationship between experimentally distinguishable elements. For example, $F=ma$ tells us that the product of the measurements for mass and acceleration will be equivalent to a measurement of the force.
\end{rem}
